Explore tumor cell classification with CellAssign

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/01-marker-genes.Rmd
update criterion for all notebooks

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::has_file("LICENSE.md"))

>>>>

```{r base paths}
# The base path for the OpenScPCA repository, found by LICENSE.md file
# can't use .git because GHA doesn't find .git
repository_base <- rprojroot::find_root(rprojroot::has_file("LICENSE.md"))

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/02-cellassign.Rmd
update criterion for all notebooks

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

>>>>

```{r base paths}
# The base path for the OpenScPCA repository, found by LICENSE.md file
# can't use .git because GHA doesn't find .git
repository_base <- rprojroot::find_root(rprojroot::has_file("LICENSE.md"))
